Spatial Reasoning and Statistical Graphics

### 2014-10-11 Paper/Draft1/TestingVisualAptitude.Rnw
mini stuff

qplot(data=lineup.summary, x=value, y=lineup, geom="point", shape=I(1), size=I(3)) + facet_wrap(~variable, scales="free_x") + xlab("Value") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + geom_smooth(method="lm") + theme_bw()
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCts.png", sep=""), width=6, height=4)

@@

\begin{figure}[htbp]\centering
\includegraphics[width=0.9\textwidth]{fig-VisReasoningAnalysisCts}
\caption[Visual Aptitude Study Results]{Scatterplots of all test scores compared to participants' scores in the lineup tests. \comment{What is the main message of these plots? Relatively strong positive correlation to all established test scores?}}\label{fig:visualaptitudects}
\end{figure}

>>>>

qplot(data=lineup.summary, x=value, y=lineup, geom="point", shape=I(1), size=I(3)) + facet_wrap(~variable, scales="free_x") + xlab("Value") + ylab("Lineup Score (# Correct - 1/19 # Incorrect)") + geom_smooth(method="lm") + theme_bw()
# same aspect ratio
ggsave(paste(imgdir, "fig-VisReasoningAnalysisCts.png", sep=""), width=6, height=6)

@@

\begin{figure}[htbp]\centering
\includegraphics[width=0.75\textwidth]{fig-VisReasoningAnalysisCts}
\caption[Visual Aptitude Study Results]{Scatterplots of all test scores compared to participants' scores in the lineup tests. \comment{What is the main message of these plots? Relatively strong positive correlation to all established test scores?}}\label{fig:visualaptitudects}
\end{figure}
